A Systematic Literature Review on Extensions to Role-Based Access Control

### 2014-02-09 paper/sections/analysis.tex
Updating sections.

\section{Motivations} \label{sec:motivations}

RQ2: What are the motivations behind the RBAC extension models?

%\subsection{Results}

@@

\section{Implementations} \label{sec:implementations}

RQ3: Do the RBAC extension models have corresponding implementations?

@@

\section{Domains} \label{sec:domains}

RQ5: What domains have RBAC extensions been created for?

%\subsection{Results}

@@

\textbf{Domain} & \textbf{Papers} & \textbf{Count} \\ \cline{1-3}
Medical Domain
&
\cite{alam06:constraint}
\cite{tzelepi01:flexible}
\cite{motta03:contextual}
\cite{ni2010privacy}
\cite{damiani2007geo}
\cite{hansen2003spatial}
\cite{samuel07:spatio-temporal}
\cite{aich09:role}
\cite{zhou2007team}
&
9 \\ \cline{1-3}
Pervasive Computing Environments
& 
\cite{huang06:pervasive}
\cite{chen08:spatio-temporal}
\cite{ray07:spatio}
&
3 \\ \cline{1-3}
Web Applications
& 
\cite{masoumzadeh2008purbac}
&
1 \\ \cline{1-3}
Mobile Computing
& 
\cite{thein2011leveraging}
\cite{zou2009crbac}
\cite{chandran05:llt}
\cite{ray07:spatio}
\cite{aich09:role}
&
5 \\ \cline{1-3}
Organizations with Many Sub-departments
& 
\cite{yamazaki04:designing}
\cite{jian2008extended}
\cite{yao2008task}
&
3 \\ \cline{1-3}
Enterprise Workflows
&
\cite{cholewka00:acontext-sensitive}
\cite{bao08:role}
\cite{zhang06:collaborative}
\cite{oh2003task}
\cite{joshi05:generalized}
&
5 \\ \cline{1-3}

@@

The predominant domain for which extension models have been generated for is that of the medical domain with 9 of 27 mentioning scenarios or requirements of that industry.
Mobile computing and enterprise workflows were each represented by five papers claiming to be influenced by the requirements for access control within these domains. The final set
of domains was pervasive computing environments and large-scale organizations with three each and web applications with one.  There were three papers~\cite{jian2008extended, aich07:STARBAC, haibo2005context} without any direct mention of a domain since Aich et al. \cite{aich09:role} fall under both the medical domain and mobile computing.

@@

\section{Generalizations} \label{sec:generalizations}

RQ6: What commonalities or generalizations exist across all categories?

>>>>

\section{RQ2: Motivations} \label{sec:motivations}

\textit{What are the motivations behind the RBAC extension models?}
\\

@@

\section{RQ3: Evaluations} \label{sec:evaluations}

\textit{How are RBAC extension models implemented and evaluated by their authors?}
\\

@@

\section{RQ4: Domains} \label{sec:domains}

\textit{What domains have RBAC extensions been created for?}
\\

@@

\textbf{Domain} & \textbf{Papers} & \textbf{Count} \\ \cline{1-3}
Medical Domain
&
\cite{alam06:constraint}
\cite{tzelepi01:flexible}
\cite{motta03:contextual}
\cite{ni2010privacy}
\cite{damiani2007geo}
\cite{hansen2003spatial}
\cite{samuel07:spatio-temporal}
\cite{aich09:role}
\cite{zhou2007team}
&
9 \\ \cline{1-3}
Pervasive Computing Environments
& 
\cite{huang06:pervasive}
\cite{chen08:spatio-temporal}
\cite{ray07:spatio}
&
3 \\ \cline{1-3}
Web Applications
& 
\cite{masoumzadeh2008purbac}
\cite{haibo05:context}
&
1 \\ \cline{1-3}
Mobile Computing
& 
\cite{thein2011leveraging}
\cite{zou2009crbac}
\cite{chandran05:llt}
\cite{ray07:spatio}
\cite{aich09:role}
&
5 \\ \cline{1-3}
Organizations with Many Sub-departments
& 
\cite{yamazaki04:designing}
\cite{jian2008extended}
\cite{yao2008task}
&
3 \\ \cline{1-3}
Enterprise Workflows
&
\cite{cholewka00:acontext-sensitive}
\cite{bao08:role}
\cite{zhang06:collaborative}
\cite{oh2003task}
\cite{joshi05:generalized}
&
5 \\ \cline{1-3}

@@

The predominant domain for which extension models have been generated for is that of the medical domain with 9 of 27 mentioning scenarios or requirements of that industry.
Mobile computing and enterprise workflows were each represented by five papers claiming to be influenced by the requirements for access control within these domains. The final set
of domains was pervasive computing environments and large-scale organizations with three each and web applications with one.  There were three papers~\cite{jian2008extended, aich07:STARBAC} without any direct mention of a domain since Aich et al. \cite{aich09:role} fall under both the medical domain and mobile computing.

@@

\section{RQ5: Generalizations} \label{sec:generalizations}

\textit{What commonalities or generalizations exist across all categories?}
\\
